---
title: "week4DavidMontalvan"
author: "David Montalvan"
date: "2020/06/24"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{week4DavidMontalvan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette the functions for the package `week4DavidMontalvan` are explained.

```{r, eval = FALSE}
library(week4DavidMontalvan)
```
## `fars_read`

`fars_read` reads the csv file with the data from
the **US National Highway Traffic Safety Administration's
Fatality Analysis Reporting System**.

```{r, eval = FALSE}
fars_read("path/to/csv")
```

## `make_filename`

`make_filename` creates a character vector using
a numeric vector with the years.

```{r, eval = FALSE}
make_file(2015)
```

## `fars_read_years`

`fars_read_years` takes a numeric vector with the
years to read.

```{r, eval = FALSE}
fars_read_years(c(2015, 2014))
```

## `fars_map_state`

`fars_map_state` takes a state number and a year and
creates a map for the subset of data corresponding
to those values.

```{r, eval = FALSE}
fars_map_state(15, 2015)
```
